---
title: "2 Sigma - RentHop EDA"
author: "Sai Karthik Varanasi"
date: "March 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tm")
library("wordcloud")
library("RColorBrewer")
library(ggplot2)
library(ggmap)
library(plotly)
library(leaflet)
```

This is a document that describes the exploratory analysis of the data provided by 2 sigma for the Kaggle Competetion.

For reproducability these are my system settings when I designed this program

```{r echo = FALSE}
print("System Info")
Sys.info()

print("Package Info")
ip <- as.data.frame(installed.packages()[,c(1,3:4)])
rownames(ip) <- NULL
ip <- ip[is.na(ip$Priority),1:2,drop=FALSE]
print(ip, row.names=FALSE)
```

Loading the Data:
(Referred form the following [link](https://www.kaggle.com/danjordan/two-sigma-connect-rental-listing-inquiries/how-to-correctly-load-data-into-r) in the competetion which shows how to load the data effectively and correctly in R) as it was effective than my way.

```{r}
packages <- c("jsonlite", "dplyr", "purrr")
purrr::walk(packages, library, character.only = TRUE, warn.conflicts = FALSE)

train.data <- fromJSON("input/train.json")

```


```{r}
# unlist every variable except `photos` and `features` and convert to tibble
vars <- setdiff(names(train.data), c("photos", "features"))
train.data <- map_at(train.data, vars, unlist) %>% tibble::as_tibble(.)
```

This completes the loading of the data into the dataset`train.data`

Looking at the Loaded data, for analysis

```{r}
head(train.data,n = 1)
```

 Looking at the various details  of the data....
```{r}
nrow(train.data)
ncol(train.data)
colnames(train.data)
#summary(train.data)
```

##Extraction of Data of Interest 


Getting The Data of interest and looking at the data extracted
```{r}
train.doi <- as.data.frame(subset(train.data,select = -c(description,photos)))
train.doi$interest_level <- as.factor(train.doi$interest_level)

#train.doi$bathrooms <- as.factor(train.doi$bathrooms)
#train.doi$bedrooms <- as.factor(train.doi$bedrooms)
#Checking the different levels of the data available 
#levels(train.doi$bathrooms)
#levels(train.doi$bedrooms)

View(train.doi)

```


##Plots:


Plotting the graphs to get a better picture of the data and various varioables involved in the dataset.,

Visualization of the total dataset and different interest levels,

```{r}
plot_intrst<- ggplot(train.doi,aes(interest_level,color = interest_level,fill=interest_level ))

pi.hist <- plot_intrst+geom_histogram(stat = "count")

pi.hist
```

For understanding the distribution of the  bedrooms through Violin plots and the jitter plots

Violin Plot:

```{r}
plot_bed <- ggplot(train.doi,aes(x=interest_level, y=bedrooms,color = interest_level))+labs(title = "Interest level vs Bedrooms",x="Interest Level", y = "# of Bedrooms")
p.violin<- plot_bed+geom_violin(trim = FALSE)
p.violin
```

Jitter Plot:

```{r}
p.jitter <- plot_bed+geom_jitter(shape=16, position=position_jitter(0.05))
p.jitter
```

For understanding the distribution of the  bathrooms through Violin plots and the jitter plots

Violin Plot:

```{r}
plot_bath <-ggplot(train.doi,aes(x=interest_level, y=bathrooms,color = interest_level))+labs(title = "Interest level vs Bedrooms",x="Interest Level", y = "# of Bedrooms")

pb.violin <- plot_bath+geom_violin(trim = FALSE)
pb.violin
```

Jitter Plot:

```{r}
pb.jitter <- plot_bath+geom_jitter(shape=16, position=position_jitter(0.05))
pb.jitter
```

For the analysis of the target variable, `interest_level` in the dataset,


```{r}
#Looking at O/p variable
unique(train.data$interest_level)

## Maps


g <- list(
        scope = 'usa',
        projection = list(type = 'albers usa'),
        showland = TRUE,
        landcolor = toRGB("gray85"),
        subunitwidth = 1,
        countrywidth = 1,
        subunitcolor = toRGB("white"),
        countrycolor = toRGB("white")
)


p <- plot_geo(train.doi, locationmode = 'USA-states', sizes = c(20, 250)) %>%
        add_markers(
                x = ~longitude, y = ~latitude, size = ~price, color = ~interest_level, hoverinfo = "text",
                text = ~paste(train.doi$display_address,",", train.doi$street_address, "<br />", train.doi$bedrooms," bed","<br />",train.doi$bathrooms, " bath")
        ) %>%
        layout(title = 'Distribution of homes wrt interest level<br>(Click legend to toggle)', geo = g)

p 
# Commeting the plot as it takes too long to process the info
#plot_details <- leaflet(train.doi) %>%  addTiles() %>% addMarkers(
#        clusterOptions = markerOptions(freezeAtZoom = 5)
#        )%>% 
#        addMarkers(~longitude, ~latitude, popup = ~paste(train.doi$display_address,",", train.doi$street_address, "<br />", train.doi$bedrooms," #bed","<br />",train.doi$bathrooms, " bath") )

#plot_details

```


Now to analyze the features that are listed for a particular datarow for understanding the data wrt features present. For this we create seperate dataframes based on the type of interest level of the customer.

```{r}
train.doih<- train.doi[train.doi$interest_level =='high',]
train.doil<- train.doi[train.doi$interest_level =='low',]
train.doim<- train.doi[train.doi$interest_level =='medium',]
```

Plotting a WordCloud and the most frequently used words in the dataset, we have


```{r}
#Word Cloud with all data
train.features <- unlist(train.doi$features,recursive = TRUE,use.names = FALSE)
train.ft <- as.data.frame(table(train.features))
names(train.ft) <- c("words","freq")
train.ft <- train.ft[with(train.ft, order(-freq)), ]

set.seed(1234)

wrd_cld<- wordcloud(words = train.ft$words, freq = train.ft$freq, min.freq = 1,
          max.words=1000, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(10,"Dark2"))
wrd_cld

plot_freqwrd<- barplot(train.ft[1:10,]$freq, las = 2, names.arg = train.ft[1:10,]$words,
        col ="lightblue", main ="Most frequent features",
        ylab = "Word frequencies")

plot_freqwrd

```




Performing similar analysis for the data for which the interest level is high


```{r}
#Word cloud with interest level as "High"

train.fthigh <- unlist(train.doih$features,recursive = TRUE,use.names = FALSE)
train.fthigh <- as.data.frame(table(train.fthigh))
names(train.fthigh) <- c("words","freq")
train.fthigh <- train.fthigh[with(train.fthigh, order(-freq)), ]

set.seed(1234)

wrd_cld_high<- wordcloud(words = train.fthigh$words, freq = train.fthigh$freq, min.freq = 1,
                    max.words=1000, random.order=FALSE, rot.per=0.35, 
                    colors=brewer.pal(10,"Dark2"))
wrd_cld_high

plot_freqwrdh<- barplot(train.ft[1:10,]$freq, las = 2, names.arg = train.fthigh[1:10,]$words,
                       col ="lightblue", main ="Most frequent features with intrst level High",
                       ylab = "Word frequencies")

plot_freqwrdh
```



For listing whose innterest level is medium

```{r}
#Word cloud with interest level as "medium"

train.ftmed <- unlist(train.doim$features,recursive = TRUE,use.names = FALSE)
train.ftmed <- as.data.frame(table(train.ftmed))
names(train.ftmed) <- c("words","freq")
train.ftmed <- train.ftmed[with(train.ftmed, order(-freq)), ]

set.seed(1234)

wrd_cld_med<- wordcloud(words = train.ftmed$words, freq = train.ftmed$freq, min.freq = 1,
                        max.words=1000, random.order=FALSE, rot.per=0.35, 
                        colors=brewer.pal(10,"Dark2"))
wrd_cld_med

plot_freqwrdm<- barplot(train.ft[1:10,]$freq, las = 2, names.arg = train.ftmed[1:10,]$words,
                        col ="lightblue", main ="Most frequent features in intrst lvl as Medium",
                        ylab = "Word frequencies")

plot_freqwrdm
```



For listings whose interst level is low,

```{r}
#Word cloud with interest level as "low"

train.ftlow <- unlist(train.doil$features,recursive = TRUE,use.names = FALSE)
train.ftlow <- as.data.frame(table(train.ftlow))
names(train.ftlow) <- c("words","freq")
train.ftlow <- train.ftlow[with(train.ftlow, order(-freq)), ]

set.seed(1234)

wrd_cld_low<- wordcloud(words = train.ftlow$words, freq = train.ftlow$freq, min.freq = 1,
                        max.words=15000, random.order=FALSE, rot.per=0.35, 
                        colors=brewer.pal(10,"Dark2"))
wrd_cld_low

plot_freqwrdl<- barplot(train.ft[1:10,]$freq, las = 2, names.arg = train.ftlow[1:10,]$words,
                        col ="lightblue", main ="Most frequent features in intrst lvl as low",
                        ylab = "Word frequencies")

plot_freqwrdl

```


 ### To be continued.......