<<<<<<< HEAD
---
title: "2 Sigma - RentHop EDA"
author: "Sai Karthik Varanasi"
date: "March 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a document that describes the exploratory analysis of the data provided by 2 sigma for the Kaggle Competetion.

For reproducability these are my system settings when I designed this program

```{r echo = FALSE}
print("System Info")
Sys.info()

print("Package Info")
ip <- as.data.frame(installed.packages()[,c(1,3:4)])
rownames(ip) <- NULL
ip <- ip[is.na(ip$Priority),1:2,drop=FALSE]
print(ip, row.names=FALSE)
```

Loading the Data:
(Referred form the following [link](https://www.kaggle.com/danjordan/two-sigma-connect-rental-listing-inquiries/how-to-correctly-load-data-into-r) in the competetion which shows how to load the data effectively and correctly in R) as it was effective than my way.

```{r}
packages <- c("jsonlite", "dplyr", "purrr")
purrr::walk(packages, library, character.only = TRUE, warn.conflicts = FALSE)

train.data <- fromJSON("input/train.json")

```


```{r}
# unlist every variable except `photos` and `features` and convert to tibble
vars <- setdiff(names(train.data), c("photos", "features"))
train.data <- map_at(train.data, vars, unlist) %>% tibble::as_tibble(.)
```

This completes the loading of the data into the dataset`train.data`

Looking at the Loaded data, for analysis

```{r}
head(train.data,n = 1)
```

```{r}
colnames(train.data)
summary(train.data)
=======
---
title: "2 Sigma - RentHop EDA"
author: "Sai Karthik Varanasi"
date: "March 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a document that describes the exploratory analysis of the data provided by 2 sigma for the Kaggle Competetion.

For reproducability these are my system settings when I designed this program

```{r echo = FALSE}
print("System Info")
Sys.info()

print("Package Info")
ip <- as.data.frame(installed.packages()[,c(1,3:4)])
rownames(ip) <- NULL
ip <- ip[is.na(ip$Priority),1:2,drop=FALSE]
print(ip, row.names=FALSE)
```

Loading the Data:
(Referred form the following [link](https://www.kaggle.com/danjordan/two-sigma-connect-rental-listing-inquiries/how-to-correctly-load-data-into-r) in the competetion which shows how to load the data effectively and correctly in R) as it was effective than my way.

```{r}
packages <- c("jsonlite", "dplyr", "purrr")
purrr::walk(packages, library, character.only = TRUE, warn.conflicts = FALSE)

train.data <- fromJSON("input/train.json")

```


```{r}
# unlist every variable except `photos` and `features` and convert to tibble
vars <- setdiff(names(train.data), c("photos", "features"))
train.data <- map_at(train.data, vars, unlist) %>% tibble::as_tibble(.)
```

This completes the loading of the data into the dataset`train.data`

Looking at the Loaded data, for analysis

```{r}
head(train.data,n = 1)
```

```{r}
colnames(train.data)
summary(train.data)
>>>>>>> 3bca7c470f8a032c311d145de8b7548faf42e0ae
```